# Persiapan Data

Bab ini menjelaskan tentang persiapan data dan dasar-dasar plotting

## Memuat pustaka

```{r 02-installation-3, message=FALSE}
# Packages for spatial data processing & visualization
library(rgdal)
library(gdalUtils)
library(raster)
library(sf)
library(sp)
library(RStoolbox)
library(getSpatialData)
library(rasterVis)
library(mapview)

library(RColorBrewer)
library(plotly)
library(grDevices)

# Machine learning packages
library(caret)
library(randomForest)
library(ranger)
library(MLmetrics)
library(nnet)
library(NeuralNetTools)
library(LiblineaR)

# Packages for general data processing and parallel computation
library(data.table)
library(dplyr)
library(stringr)
library(doParallel)
library(snow)
library(parallel)
# set the temporary folder for raster package operations
rasterOptions(tmpdir = "./cache/temp")
```

## Set Area of Interest







```{r 02-aoi-3, message=FALSE}

aoi <- matrix(data = c(22.85, 45.93,  # Upper left corner
                       22.95, 45.93,  # Upper right corner
                       22.95, 45.85,  # Bottom right corner
                       22.85, 45.85,  # Bottom left corner
                       22.85, 45.93), # Upper left corner - closure
              ncol = 2, byrow = TRUE)
set_aoi(aoi)
```

## View Area of Interest

```{r 02-aoi-3, message=FALSE}

```


```{r 02-aoi-3, message=FALSE}
view_aoi()
```


## Impor data 

```{r 02-aoi-3, message=FALSE}
fs <- list.files(path="./data", pattern = ".tif$", full.names = TRUE)
s <- raster::stack(fs)
```

## Ubah nama bands

bands <- c("B02","B03","B04","B08","B06","B07","B11","B12","B8A")

names(s) <- names(bands)

names(s) <- str_extract(sapply(bands, names),"B.{2}")

### Impor data ke QGIS


### Impor data ke R

## Mengkonversi Tabel menjadi Data Spasial

## Dasar-dasar plotting dan visualisasi data

## Ekspor data

